BVP Paper

### 2017-11-30 tex/bvp_paper.tex
more small progress on paper.

@@

>>>>

Knowledge of Mixing Length theory and the nature of evolved convection has been used in some 
previous studies (e.g., \cite{brandenburg&all2005}) to choose smarter initial conditions than
the hydrostatic polytropic states.  However, these assumptions work best in convective regions
which are bounded by stable layers.  In simple atmospheres where boundary layers form to meet
boundary conditions at the upper and lower edge of the atmosphere, we cannot know 
\emph{a priori} what the extent or shape of the boundary layer will be, as that must be chosen
by the convective dynamics, and specification of the proper boundary layer is essential for
placing the atmosphere along the proper adiabat.

@@

\subsubsection{The Boundary Value Equations}
In studies of fully compressible convection, the flux carried by the adiabatic temperature gradient
is not available for convection.  Thus, only the flux \emph{in excess} of the adiabat will drive
convection and be carried by convection.  As such, this is the only portion of the flux which
must be examined to determine if the solution is in a converged state.  In a system with
a fixed flux boundary condition, the available superadiabatic flux is
\begin{equation}
F_{\text{avail}} = -\kappa(\grad T_0 - \grad T_{\text{ad}}) = \kappa\frac{\epsilon}{c_P}\grad T_0,
\end{equation}
which is small when $\epsilon$ is small and only requires low Mach number convective flows
to carry it.  In a perfectly evolved solution, there will be thin boundary layers in which
conduction carries this flux in addition to the adiabatic flux, but in an efficient convective
interior, convective fluxes must carry this full amount.

The BVP equations are inspired by equations of stellar modeling  \cite{paxton&all2011} but adapted to these simulations
of fully compressible convection.  Here, rather than parameterizing convection, we can get the
convective fluxes directly from our simulation adn use them to solve for the appropriate structure
of the atmosphere.  The FC BVP equations are
\begin{gather}
\frac{d M_1}{dz} = \rho_1 \\
T_0 \grad \rho_1 + T_1 \grad \rho_0 + \rho_1 g = - T_0 \grad \rho_0 - T_1 \grad \rho_1 - \rho_0 g \\
\kappa \frac{d^2 T_1}{d z^2} = -\frac{d}{dz}F_{\text{conv, z}},
\end{gather}
which ensure mass conservation, thermal equilibrium, and that the atmosphere is, on average,
in hydrostatic equilibrium.  We couple these equations with four boundary conditions (mixed
flux / temperature boundary conditions, as well as setting $M_1 = 0$ at the top and bottom
of the atmosphere).
